---
title: "Using Rmarkdown and Github for Reproducible Research"
author: "Jinliang Yang"
date: "November 18, 2014"
output: 
  beamer_presentation:
    theme: "AnnArbor"
    colortheme: "dolphin"
    fonttheme: "structurebold"
---

## People behind part of this work

\graphicspath{{../graphs/}}
\begin{figure}
\includegraphics{guys.png}
\caption{}
\label{fig:mfig1}
\end{figure}

## A show case of Markdown

- **markdown**: a simple plain text format originally designed for html translation.  
The syntax of [_markdown_](http://0.0.0.0:4000/reproducible/2014/11/05/reproducible-research/) is as simple as only one page.

- **Jekyll**: a static websites generator using **markdown**  
see a toy [_website_](http://0.0.0.0:4000) served by [_Jekyll_](http://jekyllrb.com/)  
  
- Free hosting with **Github pages** with a **gh-pages** branch  

## A show case of Rmarkdown

- Documents  
  Create _HTML_, _PDF_ and _MS Word_ Documents via **RStudio**

- Presentation  
  Create _Beamer_, _ioslides_ and _Slidy_ presentations.

Yihui developed this R package **knitr**, which enables Rmarkdown to include any embedded R code chunks via **Pandoc**. 

## R code chunks options
- Code evaluation, docoration and plots {r, eval=TRUE, echo=TRUE} 
```{r, eval=TRUE, fig.height=4, fig.width=7}
x <- seq(-4, 4, length=100)
hx <- dnorm(x)
plot(x, hx, type="l", lty=2, ylab="Density", 
     main="A t Distribution")
```


## Setup your project

- using __GitHub__ to do the version control
- using **packrat** to do the R package dependency management
- using **ProjectTemplate** to layout working directories  

```{r, eval=FALSE}
#install.packages('ProjectTemplate')
library('ProjectTemplate')
create.project('temp')
system("mv temp/* .")
system("rm -r temp/")
```
Or just copy your favorite `directory` into the project!

## Setup your project
\graphicspath{{../graphs/}}
\begin{figure}
\includegraphics{dir.png}
\caption{Your directory system}
\label{fig:mfig2}
\end{figure}

## Notes for better reproducible

- Use relative path not absolute path
- **source** your codes rather than embedded as R code chunks
- Turn off the R code evaluation for computational heavy work
- gitignore large data
- for non-R codes, refering **shell** scripts

## More notes about general programming

- Small is beautiful.
- Make each program do one thing well.
- Build a prototype as soon as possible.
- Choose portability over efficiency.
- Store data in flat text files.
- Use shell scripts to increase leverage and portability.

By Mike Gancarz (1994)

